Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-06-17 thesis/chapters/ch_chapter4.tex
Correcting appendix figure numbering
edits

The elemental abundances of a galaxy over time are sensitive to the nuclear physics and stellar astrophysics that determines which stars make what elements and when. The stellar abundance patterns within a given galaxy also depend on the details of how those metals are released into the ISM through various forms of stellar feedback, and the hydrodynamic interactions that ultimately mix those elements into the ISM or eject them from the galaxy in galactic winds. Stellar abundance patterns in old, metal poor systems are the result of enrichment from substantially fewer sources than younger, more metal rich stellar populations. Because of this, studying abundance patterns in these environments allows us to place constraints on the yields of individual enrichment events and the nucleosynthetic sites of each element. The lowest mass dwarf galaxies in the Local Group, UFDs, offer some of the best constraints on these processes. These environments can potentially be used to trace and constrain enrichment from the first stars \citep[e.g.][]{FrebelBromm2012,Ji2015,Ritter2015,Jeon2017,Hartwig2018} and have been used to place constraints on the variety of possible astrophysical sources of r-process enrichment \citep[e.g.][]{Ji2016a,Ji2016b,Ji2018a,Ji2019,Tsujimoto2017,Duggan2018,Nagasawa2018,Ojima2018}. It is likely that chemical enrichment in more massive, metal rich systems with ongoing star formation like the Milky Way exhibits smaller abundance spreads. The size of more massive galaxies reduces the relevance of stochasticity, averaging over the variety of complex hydrodynamics and feedback-driven turbulence that may be driving much of the significant vgariance in stellar abundances seen at low metallicity. Stochasticity, which has been shown to be important for setting the width of stellar abundance patterns in low metallicity environments of the Milky Way halo \citep[e.g.][]{Cescutti2008,Cescutti2014}, plays an even greater role in the evolution of these low mass dwarf galaxies \citep{Applebaum2018}. Indeed the increase in scatter in the stellar abundance patterns of low mass dwarf galaxies and UFDs has been attributed to inhomogeneous mixing and stochastic effects \citep[e.g.][]{Norris2010a,Lee2013,Simon2015,Mashonkina2017,Suda2017}. This complicates the interpretation of abundance patterns in these galaxies, particularly for constraining individual enrichment events.

@@

%\clearpage
%\appendix - Liklely DO NOT use this command
\setcounter{section}{0}%
\renewcommand\thesection{\thechapter.\Alph{section}}

>>>>

The elemental abundances of a galaxy over time are sensitive to the nuclear physics and stellar astrophysics that determines which stars make what elements and when. The stellar abundance patterns within a given galaxy also depend on the details of how those metals are released into the ISM through various forms of stellar feedback, and the hydrodynamic interactions that ultimately mix those elements into the ISM or eject them from the galaxy in galactic winds. Stellar abundance patterns in old, metal poor systems are the result of enrichment from substantially fewer sources than younger, more metal rich stellar populations. Because of this, studying abundance patterns in these environments allows us to place constraints on the yields of individual enrichment events and the nucleosynthetic sites of each element. The lowest mass dwarf galaxies in the Local Group, UFDs, offer some of the best constraints on these processes. These environments can potentially be used to trace and constrain enrichment from the first stars \citep[e.g.][]{FrebelBromm2012,Ji2015,Ritter2015,Jeon2017,Hartwig2018} and have been used to place constraints on the variety of possible astrophysical sources of r-process enrichment \citep[e.g.][]{Ji2016a,Ji2016b,Ji2018a,Ji2019,Tsujimoto2017,Duggan2018,Nagasawa2018,Ojima2018}. It is likely that chemical enrichment in more massive, metal rich systems with ongoing star formation like the Milky Way exhibits smaller abundance spreads. The size of more massive galaxies reduces the relevance of stochasticity, averaging over the variety of complex hydrodynamics and feedback-driven turbulence that may be driving much of the variance in stellar abundances seen at low metallicity. Stochasticity, which has been shown to be important for setting the width of stellar abundance patterns in low metallicity environments of the Milky Way halo \citep[e.g.][]{Cescutti2008,Cescutti2014}, plays an even greater role in the evolution of these low mass dwarf galaxies \citep{Applebaum2018}. Indeed the increase in scatter in the stellar abundance patterns of low mass dwarf galaxies and UFDs has been attributed to inhomogeneous mixing and stochastic effects \citep[e.g.][]{Norris2010a,Lee2013,Simon2015,Mashonkina2017,Suda2017}. This complicates the interpretation of abundance patterns in these galaxies, particularly for constraining individual enrichment events.

@@

%\clearpage
%\appendix - Liklely DO NOT use this command
\setcounter{section}{0}%
\renewcommand\thesection{\thechapter.\Alph{section}}
\counterwithin{figure}{section}
